From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Added new screenshot with external dataset.

In the following months, we progressively added more statements to the tool's database back-end.
Thereby, we were able to slowly upscale the tool's database back-end
without risking back-end performance bottlenecks.
The process of adding data in small batches of 1~million to 2~million statements per batch
further allowed us to detect some potential issues in the front-end
and fix them before they became actual problems.
Another positive side-effect of this approach was that it allowed us to gather quick feedback
from the community about the already mapped data and thus to adapt the mapping scripts early
and correct minor issues with the data in the back-end.

@@

@@

\section{Future Work and Conclusion}\label{sec:future-work-and-conclusion}

The largest gains for the migration can be achieved
by extending the mapping to more Freebase topics.
A~possible way of realizing this is to create a~user interface%
---possibly leveraging elements of gamification---%
that would allow users to create new Wikidata items for a~suggested topic
or to add a~mapping for them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata,
we could rank the topics that are not mapped yet by the number of incoming links
from already mapped topics and filter less interesting types like ISBNs.

Another area for improvement is to upload high quality datasets using a~bot,
like the reviewed facts or some sets for external IDs,
in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have also started to import labels that are in Freebase and are absent from Wikidata.
In the 17.2~million Freebase labels for mapped topics,
only 0.9~million, \emph{i.e.}, 5\%, are missing in Wikidata.

Concluding, in a~fairly short amount of time, we have been able
to provide the Wikidata community with more than\linebreak 14~million new Wikidata statements
using a~customizable and generalizable approach, consisting of data preparation scripts
and the \emph{Primary Sources Tool},
which is well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty of having adequate metrics to measure the size of knowledge bases
in a~meaningful way,
and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.
We hope that with the help of the \emph{Primary Sources Tool} and
the Freebase dataset---and in future also other datasets---%
we will increase the completeness and accuracy of Wikidata.

>>>>

In the following months, we progressively added more statements to the tool's database back-end.
Thereby, we were able to slowly upscale the tool's database back-end
without risking back-end performance bottlenecks,
and so far, scale or throughput have not been a~problem.
The process of adding data in small batches of 1~million to 2~million statements per batch
further allowed us to detect some potential issues in the front-end
and fix them before they became actual problems.
Another positive side-effect of this approach was that it allowed us to gather quick feedback
from the community about the already mapped data and thus to adapt the mapping scripts early
and correct minor issues with the data in the back-end.

@@

\subsection{Usage with Other Datasets}

As outlined earlier, the \emph{Primary Sources Tool} from the start was designed to be used
with other datasets apart from the Freebase dataset.
A~concrete first example is the ``FBK StrepHit Soccer'' dataset,%
\footnote{``FBK StrepHit Soccer'' dataset:
\url{https://lists.wikimedia.org/pipermail/wikidata/2015-September/007014.html}}
which, among other datasets, can be activated in the tool by clicking on its gears icon.
The dataset selection dialog is depicted in \autoref{fig:soccer},
as well as facts coming from this dataset.
It is also possible to activate all datasets at once in parallel.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.93\columnwidth]{img/fbk-strephit-soccer.pdf}
    \caption{\emph{Primary Sources Tool} used with the ``FBK StrepHit Soccer'' dataset,
    the screenshot shows the dataset selection dialog and incoming facts from this dataset.}
    \label{fig:soccer}
\end{figure}

@@

\section{Future Work and Conclusions}\label{sec:future-work-and-conclusion}

The largest gains for the migration can be achieved
by extending the mapping to more Freebase topics.
A~possible way of realizing this is to create a~user interface%
---possibly leveraging elements of gamification---%
that would allow users to create new Wikidata items for a~suggested topic
or to add a~mapping for them to an existing Wikidata item.
In order to suggest interesting topics to add to Wikidata,
we could rank the topics that are not mapped yet by the number of incoming links
from already mapped topics and filter less interesting types like ISBNs.
Another area for improvement is to upload high quality datasets using a~bot,
like the reviewed facts or some sets for external IDs,
in order to speed up the integration of Freebase content into Wikidata.
We have already started to upload simple reviewed facts about humans
like birth date, death place or gender using a~bot.
We have started to import labels that are in Freebase but not in Wikidata.
In the 17.2~million Freebase labels for mapped topics,
only 0.9~million, \emph{i.e.}, 5\%, lack from Wikidata.

Concluding, in a~fairly short amount of time, we have been able
to provide the Wikidata community with more than\linebreak 14~million new Wikidata statements
using a~customizable and generalizable approach, consisting of data preparation scripts
and the \emph{Primary Sources Tool},
which is well integrated into the Wikidata user interface.
The effort needed to map two fairly different knowledge bases has also been a~good occasion
to highlight the difficulty of having adequate metrics to measure the size of knowledge bases
in a~meaningful way,
and, in consequence, the ``value'' of such collaborative knowledge bases and the datasets added to them.
We hope that with the help of the \emph{Primary Sources Tool} and
the Freebase dataset---and in future even more datasets---%
we will increase the completeness and accuracy of Wikidata.
